### 2014-04-30 paper.tex
Merged QP into QuadProg++

@@

\section{Hardware}
\subsection{Atlas}

@@

@@

\subsection{QuadProg++}
QuadProg++[http://quadprog.sourceforge.net/] is a quadratic programming solver. The algorithm implements the Goldfarb-Idnani active-set dual method. At present it is limited to the solution of strictly convex quadratic programs. \cite{quadprog}

@@

The

@@

\section{Acknowledgment}
(TODO: Special thanks to NVIDIA)

>>>>

Thank you Carnegie Mellon University, with special consideration towards Eric Whitman, Chris Atkeson, and Siyuan Feng, for that without your help on the development on the controller, and many of the amazing motions that Atlas is able to achieve today.

Lastly, thanks to the Nvidia Corporation for providing Worcester Polytechnic Institute for top of line graphical processing units.

@@

\section{Hardware}
\subsection{Atlas}
\begin{wrapfigure}{r}{0.3\textwidth}
  \begin{center}
    \includegraphics[scale=0.2]{images/atlas_joints.png}
  \end{center}
  \caption{Atlas' set of joints}
\end{wrapfigure}

@@

Robot Operational System (ROS) is a messaging messaging software that allows for remote procedure calls (RPC) through pre-defined message definitions. The basics of the framework allows for nodes to publish messages on given names, and any other piece of software on the network can listen to the message by knowing the name of published message.

For example, an important piece of software, TF, listens to messages about the robot joint states, and with additional information about kinematic model, publishing information about the transformation matrices between each frame of reference between on the body.

@@

QuadProg++[http://quadprog.sourceforge.net/] is a quadratic programming solver. The algorithm implements the Goldfarb-Idnani active-set dual method. At present it is limited to the solution of strictly convex quadratic programs. \cite{quadprog}

@@

@@
